---
title: "exercise-10"
author: "Jyhreh Johnson"
date: "4/7/2022"
output: 
  html_document: 
    highlight: zenburn
    theme: readable
---
1. Load in the Kamilar and Cooper (2013) dataset.
```{r}
library(tidyverse)
library(ggpubr)
library(ggplot2)
f <- "https://raw.githubusercontent.com/difiore/ada-2022-datasets/main/KamilarAndCooperData.csv"
d <- read_csv(f, col_names = TRUE)
head(d)
```

2. Plot lifespan (MaxLongevity_m) versus female body mass (Body mass female mean).
```{r}
#Plot lifespan v body mass
par(mfrow = c(2, 2))
plot(d$Body_mass_female_mean, d$MaxLongevity_m)
plot(log(d$Body_mass_female_mean), d$MaxLongevity_m)
plot(log(d$Body_mass_female_mean), log(d$MaxLongevity_m))
```
**Question** Is the relationship linear?
- The relationship of the last two plots do appear to be linear, while the first plot does not show a linear relationship.

**Question** How might you transform?
-

3. Run linear models of lifespan ~ female body mass, lifespan ~ log(female body mass), and log(lifespan) ~ log(female body mass).
```{r}
#Create the models
ls_m1 <- lm(data = d, MaxLongevity_m ~ Body_mass_female_mean)
ls_m2 <- lm(data = d, MaxLongevity_m ~ log(Body_mass_female_mean))
ls_m3 <- lm(data = d, log(MaxLongevity_m) ~ log(Body_mass_female_mean))

ls_m1
ls_m2
ls_m3
```

4. Generate the residuals for all three linear models, plot them in relation to the corresponding explanatory variable, and make histograms of the residuals.
```{r}
#Find the residuals
m1_res <- ls_m1$residuals
m2_res <- ls_m2$residuals
m3_res <- ls_m3$residuals

m1_res
m2_res
m3_res

#Plot them in relation to the corresponding explanatory variable
par(mfrow = c(2, 2))
plot(ls_m1$model$Body_mass_female_mean, m1_res)
plot(ls_m2$model$`log(Body_mass_female_mean)`, m2_res) 
plot(ls_m3$model$`log(Body_mass_female_mean)`, m3_res)

#make histograms
par(mfrow = c(2, 2))
hist(m1_res, xlim = c(-4 * sd(m1_res), 4 * sd(m1_res)), breaks = 20, main = "Histogram of Lifespan (Model 1) Residuals")

hist(m2_res, xlim = c(-4 * sd(m2_res), 4 * sd(m2_res)), breaks = 20, main = "Histogram of Lifespan (Model 2) Residuals")

hist(m3_res, xlim = c(-4 * sd(m3_res), 4 * sd(m3_res)), breaks = 20, main = "Histogram of Lifespan (Model 3) Residuals")
```
**Question** Do they appear to be normally distributed?
- The histograms do seem to be normally distributed.

5. Generate the QQ plots for all three linear models. 
```{r}
#Create QQ Plots
ggqqplot(ls_m1$residuals)
ggqqplot(ls_m2$residuals)
ggqqplot(ls_m3$residuals)
```
**Question** Do they appear to be normally distributed?
- Yes

6. Run the plot command for all three models. 
```{r}
par(mfrow = c(2, 2))
plot(ls_m1)
plot(ls_m2)
plot(ls_m3)
```
**Question** What do the plots suggest?
-ls_m1: According to the plots, 

7. Run a Shapiro-Wilk test on residuals for all three models.
```{r}
#Run the Shapiro-Wilk test
s1 <- shapiro.test(ls_m1$residuals)
s2 <- shapiro.test(ls_m2$residuals)
s3 <- shapiro.test(ls_m3$residuals)

s1
s2
s3
```

**Question** What do results suggest?
-